\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\begin{document}
\noindent Yang Zhicheng \\{}
Jilin Jianzhu University, Changchun, China \\{}
[\texttt{your-email@jlju.edu.cn}] \\[6pt]
\noindent Date: July 8, 2026 \\[12pt]

\noindent To the Editorial Office of \\
\textit{Communications in Mathematics and Statistics} \\[12pt]

\noindent Dear Editor-in-Chief and Editorial Board, \\[6pt]

Please find enclosed our original research article entitled

\begin{quote}
\textbf{``A Robust Median-of-Means Test for High-Dimensional Mean Vectors with Heavy-Tailed Noise''}
\end{quote}

for consideration for publication in \textit{Communications in Mathematics and Statistics}.

The manuscript addresses high-dimensional mean-vector testing under heavy-tailed noise, where
classical Hotelling's $T^{2}$ is undefined when $p\ge n$ and popular moment-based high-dimensional
tests lose their nominal size. We propose a median-of-means test that splits the sample into
blocks, replaces each coordinate's mean by the coordinate-wise median of block means, debiases the
squared norm by the between-block spread, and calibrates the null through a Rademacher multiplier
bootstrap. We establish bootstrap validity, level-$\alpha$ control, and a consistency result, and
demonstrate by Monte Carlo simulation ($B=500$) that the test attains the nominal $0.05$ level
under Gaussian, $t(5)$ and $t(3)$ noise while the competing Bai--Saranadasa test collapses to
near-zero size under heavy tails. The work is original, has not been published elsewhere, and is
not under consideration by another journal. All numerical results are fully reported in the
manuscript and its simulation code and generated results, archived as Supplementary Material.

We confirm that all authors have approved the manuscript and consent to its submission, and we have
no competing interests to declare. [Adjust the Statements and Declarations in the manuscript if your
circumstances differ.]

Thank you for your consideration. We look forward to your response. \\[6pt]

\noindent Sincerely, \\[6pt]
\noindent Yang Zhicheng (corresponding author) \\{}
[On behalf of all authors]

% Note: the manuscript (manuscript.tex) already contains the structured abstract (Purpose/Methods/
% Results/Conclusion), MSC codes, Keywords, and the Statements and Declarations + Acknowledgements
% required by the journal. Compile with: pdflatex manuscript && bibtex manuscript && pdflatex manuscript && pdflatex manuscript.
\end{document}
